\newpage
\section{Presentations}
Due to limited time, classes will mostly focus on diffusive mass transfer, however convective mass transfer is also an important mode of mass transport. Your task is to undertake a research project to learn about convective mass transfer, and then present to the class about any application of convective mass transfer that you find interesting. Presentation time will be 8 minutes. Chapter 9 of the book has a good summary of the subject.

For maximum marks you should do the following:

\begin{itemize}
    \item Ensure that your presentation is 7:00-8:00 minutes long. Timing will be stricly kept.
    \item Include a basic description of equations related to your chosen subject.
    \item Include at least 1 graph.
    \item Clearly demonstrate understanding (showing calculation examples is a good way to do this).
    \item Demonstrate a novel application of convective heat mass transfer.
    \item Ensure the work is your own and you cite all references, as well as images and text taken from other sources.
    \item Pitch the presentation at a level whereby your classmates can follow your discussion.
    \item Explain accuratly and clearly.
    \item Talk in either English or Japanese.
    \item Write any text on the slides mostly (90\%+) in English.
\end{itemize}

\emph{Note: The application that you describe can does not have to be originally invented by you (although you are welcome to propose an application like this if you wish). The application may already exist, but you will need to demonstrate understanding about the application and calculations involved in the use of convective mass transfer.}
